Towards a Machine Learning approach for Aggregate Computing

### 2021-11-04 paper-2021-woa-ac-ml.tex
Remove generated stuff + fix affiliations
Beginning of intro

\newcommand{\unibo}{\textsc{Alma Mater Studiorum} -- \textit{Università di Bologna}}
\newcommand{\disi}{\textit{Computer Science and Engineering - DISI}}
\newcommand{\scafi}{{ScaFi}}
\newcommand{\scalaloci}{{ScalaLoci}}
\newcommand{\scafiloci}{{ScaFiLoci}}
\newcommand{\scalainline}[1]{\mintinline[fontsize=\small]{scala}{#1}}
%%%%% LEGENDA FOR NOTES %%%%%
%% RED: constraints
%% YELLOW: suggestions
%% CYAN: todos
%% GREEN: outline
\newcommand{\constraints}[1]{\todo[inline, color=red]{#1}}
\newcommand{\suggestions}[1]{\todo[inline, color=yellow]{#1}}
\newcommand{\todos}[1]{\todo[inline, color=cyan]{#1}}
\newcommand{\outline}[1]{\todo[inline, color=green]{#1}}
%% Utility commands
\newcommand{\hybridaggregate}{\textit{Hybrid Aggregate Computing}}
\newcommand{\round}{\texttt{round}}
\newcommand{\export}{\texttt{export}}

@@

\maketitle
\begin{abstract}
\suggestions{}
Artificial intelligence is here to stay. 
 In particular, Deep Learning techniques in the last years outperform 
 hand-craft human solutions in different contexts, ranging from computer vision to videogames.
%
Currently, though, an all-encompassing Deep learning algorithm does not exist, 
 so researchers explore the possibility to apply these techniques in different fields.

@@

\suggestions{Perhaps we could change the narration directly towards "reinforcement learning". I think that I cannot continue to explore multiple solutions..}
\section{Introduction}
Nowadays, computer engineers have to deal with Collective Adaptive Systems (CASs)
 due to the increasing interconnected computational devices placed in ever-changing environments.
 Examples of those include robot swarm, smart cities and augmenting crowds.

CASs are characterised by 
\begin{itemize}
\item a global order that emerges from local node interactions, 
\item  decentralised control, and 
\item adaptive behaviours towards environmental changes to pursuit a collective goal.
\end{itemize}
CAS are notoriously hard to design due as part of complex systems. 
%
So, over the years, in literature, various approaches aim at handling this complexity. 
%
Some of them take inspiration from the natural system
 composed of social animals --- like bees, fish and ants. 
%
Here, a sort of hive mind arises -- 
 something referred to as swarm intelligence -- 
born from local interactions between agents. 
%
This kind of behaviour is called self-organisation, 
 namely a global order that emerges from continuous 
 interactions between simple entities.

>>>>

\newcommand{\unibo}{\textsc{Alma Mater Studiorum} -- \textit{Università di Bologna}}
\newcommand{\disi}{\textit{Computer Science and Engineering - DISI}}
\newcommand{\scafi}{{ScaFi}}
\newcommand{\scalaloci}{{ScalaLoci}}
\newcommand{\scafiloci}{{ScaFiLoci}}
\newcommand{\scalainline}[1]{\mintinline[fontsize=\small]{scala}{#1}}

%%%%% LEGENDA FOR NOTES %%%%%
%% RED: constraints
%% YELLOW: suggestions
%% CYAN: todos
%% GREEN: outline
\newcommand{\constraints}[1]{\todo[inline, color=red]{#1}}
\newcommand{\suggestions}[1]{\todo[inline, color=yellow]{#1}}
\newcommand{\todos}[1]{\todo[inline, color=cyan]{#1}}
\newcommand{\outline}[1]{\todo[inline, color=green]{#1}}
%% Utility commands
\newcommand{\hybridaggregate}{\textit{Hybrid Aggregate Computing}}
\newcommand{\round}{\texttt{round}}
\newcommand{\export}{\texttt{export}}

@@

\maketitle
\begin{abstract}
Artificial intelligence is here to stay. 
 In particular, Deep Learning techniques in the last years outperform 
 hand-craft human solutions in different contexts, ranging from computer vision to videogames.
%
Currently, though, an all-encompassing Deep learning algorithm does not exist, 
 so researchers explore the possibility to apply these techniques in different fields.

@@

\suggestions{Perhaps we could change the narration directly towards "reinforcement learning". I think that I cannot continue to explore multiple solutions..}

\section{Introduction}

Recent trends like pervasive and autonomic computing 
 promote a vision of artificially designed Collective Adaptive Systems (CASs),
 namely collections of agents coordinating and adapting %as wholes 
 to pursue joint goals in changing environments.
% due to the increasing interconnected computational devices placed in ever-changing environments.
 Examples of CASs include robot swarms, smart cities, and digitally-augmented crowds.
%
%CASs are characterised by 
%\begin{itemize}
%\item a global order that emerges from local node interactions, 
%\item  decentralised control, and 
%\item adaptive behaviours towards environmental changes to pursuit a collective goal.
%\end{itemize}
%
CAS are notoriously hard to design and control 
 %due to as part of complex systems
 as globally desired behaviour
 has to emerge from local behaviours and interactions. 
%
So, over the years, in literature, various approaches aim at handling this complexity. 
%
Some of them take inspiration from the natural system
 composed of social animals --- like bees, fish and ants. 
%
Here, a sort of hive mind arises -- 
 something referred to as swarm intelligence -- 
born from local interactions between agents. 
%
This kind of behaviour is called self-organisation, 
 namely a global order that emerges from continuous 
 interactions between simple entities.
